Millions of Type Errors

### 2023-03-22 oopsla23/paper.tex
Reanonymized
Highlight missing numbers
data: first-glance summary table

% \documentclass[acmsmall,review,anonymous]{acmart}
\documentclass[acmsmall,review]{acmart}

@@

\anon{Roblox} is a platform for \anon{shared virtual experiences},
with 56~million Daily Active Users, and 49~billion hours of engagement in
2022~\anon[(ANONYMIZED CITATION)]{\cite{roblox-quarterly-results}}.
There are XX~million creators using \anon{Roblox Studio},
and YY~million creations.

@@

@@

@@

>>>>

\documentclass[
  acmsmall,
  review,
  anonymous,
]{acmart}

@@

\anon{Roblox} is a platform for \anon{shared virtual experiences},
with 56~million Daily Active Users, and 49~billion hours of engagement in
2022~\anon[(ANONYMIZED CITATION)]{\cite{roblox-quarterly-results}}.
There are \textbf{XX}~million creators using \anon{Roblox Studio},
and \textbf{YY}~million creations.

@@

\begin{table}[t]
  \caption{Dataset overview}
  \label{t:dataset-overview}
\begin{tabular}{rl}
 5,108 & total logs \\
       & 4,574 nocheck + 510 nonstrict + 24 strict \\
 182,247 & total forced strict type errors \\
       & {113,274 in module, 6,425 in edit regions} \\
  1,521 & total type errors \\
       & {1,485 in module, 331 in edit regions}
  \\[2ex]

  1,146 & sessions \\
  & \begin{tabular}{rl}
      1,143 & single mode = 1046 nocheck + 94 nonstrict + 3 strict \\
      7 & multi mode projects \\
      3 & mode upgrades \\
      4 & mode downgrades
    \end{tabular}
\end{tabular}
\end{table}

@@

\paragraph{Research on Errors}

@@

\paragraph{Telemetry}

Transparent telemetry: explain what it is and contrast our approach.
What essential, non-transparent things did we collect?

TT =
no user ID, no machine ID,
no time-ordered traces,
public process to decide what to collect

https://research.swtch.com/telemetry-intro
